Sample size

### 2021-04-12 scripts/r/sample-size/sample-size.Rmd
:sparkles: - sample size calculation

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(brms)
library(extraDistr)
library(HDInterval)
library(tidybayes)
```

@@

```{r run-sims}
sims <- tibble(
  team_sd = seq(0.01, 0.9, by = 0.05),
  model = map(
    team_sd,
    run_simulations
  )
)

@@

saveRDS(sims_40, "./models/sim/sims_40.rds")
```

@@

```{r plot}
tibble(
  team_sd = seq(0.01, 0.9, by = 0.05),
  sd = sds,
  min = sapply(sds, function(.x) inverseCDF(0.025, phcauchy, .x)),
  max = sapply(sds, function(.x) inverseCDF(0.975, phcauchy, .x)),
  width = max - min
) %>%
  ggplot(aes(team_sd, width)) +
  geom_point(size = 5) +
  geom_segment(aes(xend = team_sd, yend = 0))

ggsave("./figs/sds_12.pdf", width = 7, height = 5)

tibble(
  team_sd = seq(0.01, 0.9, by = 0.05),
  sd = sds_20,
  min = sapply(sds_20, function(.x) inverseCDF(0.025, phcauchy, .x)),
  max = sapply(sds_20, function(.x) inverseCDF(0.975, phcauchy, .x)),
  width = max - min
) %>%
  ggplot(aes(team_sd, width)) +
  geom_point(size = 5) +
  geom_segment(aes(xend = team_sd, yend = 0))

ggsave("./figs/sds_20.pdf", width = 7, height = 5)

tibble(
  team_sd = seq(0.01, 0.9, by = 0.05),
  sd = sds_40,
  min = sapply(sds_40, function(.x) inverseCDF(0.025, phcauchy, .x)),
  max = sapply(sds_40, function(.x) inverseCDF(0.975, phcauchy, .x)),
  width = max - min
) %>%
  ggplot(aes(team_sd, width)) +
  geom_point(size = 5) +
  geom_segment(aes(xend = team_sd, yend = 0))

ggsave("./figs/sds_40.pdf", width = 7, height = 5)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
theme_set(theme_light())
library(brms)
library(extraDistr)
library(HDInterval)
library(tidybayes)
```

```{r}
dir.create("./figs/sample-size", FALSE)
```

@@

```{r run-sims}
if (file.exists("./models/sim/sims_40.rds")) {
  sims <- readRDS("./models/sim/sims.rds")
  sims_20 <- readRDS("./models/sim/sims_20.rds")
  sims_40 <- readRDS("./models/sim/sims_40.rds")
} else {
  sims <- tibble(
    team_sd = seq(0.01, 0.9, by = 0.05),
    model = map(
      team_sd,
      run_simulations
    )
  )

@@

  saveRDS(sims_40, "./models/sim/sims_40.rds")
}
```

@@

```{r plot}
sd_12 <- tibble(
  team_sd = seq(0.01, 0.9, by = 0.05),
  sd = sds,
  min = sapply(sds, function(.x) inverseCDF(0.025, phcauchy, .x)),
  max = sapply(sds, function(.x) inverseCDF(0.975, phcauchy, .x)),
  width = max - min,
  n = 12
)

sd_20 <- tibble(
  team_sd = seq(0.01, 0.9, by = 0.05),
  sd = sds_20,
  min = sapply(sds_20, function(.x) inverseCDF(0.025, phcauchy, .x)),
  max = sapply(sds_20, function(.x) inverseCDF(0.975, phcauchy, .x)),
  width = max - min,
  n = 20
)

sd_40 <- tibble(
  team_sd = seq(0.01, 0.9, by = 0.05),
  sd = sds_40,
  min = sapply(sds_40, function(.x) inverseCDF(0.025, phcauchy, .x)),
  max = sapply(sds_40, function(.x) inverseCDF(0.975, phcauchy, .x)),
  width = max - min,
  n = 40
)

bind_rows(sd_12, sd_20, sd_40) %>%
  ggplot(aes(team_sd, width, colour = as.factor(n))) +
  geom_line() +
  geom_point(size = 4) +
  geom_hline(yintercept = 1) +
  annotate("text", 0.9, 1.3, label = "1 SD") +
  geom_hline(yintercept = 2, linetype = "dashed") +
  annotate("text", 0.9, 2.3, label = "2 SD") +
  geom_hline(yintercept = 3, linetype = "dotted") +
  annotate("text", 0.9, 3.3, label = "3 SD") +
  ylim(0, 8) +
  scale_color_brewer() +
  labs(
    title = "95% CrI width depending on teams' true SD and number of teams",
    x = "Teams' true standard deviation",
    y = "95% CrI width (standard units)",
    colour = "N of teams"
  )

ggsave("./figs/sample-size/cri-width-nteams-true-sd.pdf", width = 7, height = 5)
```
